\documentclass{beamer}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{listings}
% Use Unipd as theme, with options:
% - pageofpages: define the separation symbol of the footer page of pages (e.g.: of, di, /, default: of)
% - logo: position another logo near the Unipd logo in the title page (e.g. department logo), passing the second logo path as option 
% Use the environment lastframe to add the endframe text
%\usetheme[pageofpages=of, logo=dm_logo.png]{Unipd}
\usetheme[pageofpages=of]{Unipd}

\title{Runtimes for Concurrency and Distribution}
\subtitle{Project: Exploration of orchestration challenges in a microservice-based application}
\author{Luca Marchiori}
\date{June 2024}

\lstdefinestyle{mystyle}{
    basicstyle=\ttfamily\tiny,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=1,
	aboveskip=5pt, % set the space above the lstlisting block
	belowskip=5pt, % set the space below the lstlisting block
}
\lstset{style=mystyle}


\begin{document}

\maketitle

\begin{frame}{Outline}
	\tableofcontents
\end{frame}


\section{Report corrections}
\section{Take-home message}
\begin{frame}{Take-home message}
\end{frame}
\section{Learning outcome}
\begin{frame}{Learning outcome}
\end{frame}
\section{CFU evaluation}
\begin{frame}{CFU evaluation}
	6 CFU equals to 150 hours of work.
	\\
	How I spent my time:
	\begin{itemize}
		\item Lessons: $\sim$ 48 hours
		\item Study: $\sim$ 50 hours
		\item Project: 10 weeks, $\sim$ 6/8 hours per week (60 hours)
	\end{itemize}
	\begin{block}{}
		Good balance between lessons and project, consistent with the CFU assigned.
	\end{block}
\end{frame}

\section{Feedback on the course}
\begin{frame}{Feedback on the course}
	\begin{block}{Good points}
		\begin{itemize}
			\item Very interesting topics that connect basic C.S. concepts with more advanced and real-world applications.
			\item I enjoyed the interactions between the students and the professor, especially for flipped classroom lessons.
			\item It would have been interesting to have more discussion sessions.
		\end{itemize}
	\end{block}
	\begin{block}{Improvements}
		\begin{itemize}
			\item I felt a little lost during the project development. It is hard to start from scratch without a clear idea of what are the expectations.
		\end{itemize}
	\end{block}
\end{frame}


\setbeamercolor{background canvas}{bg=red_unipd}
\begin{frame}{}
	\begin{center}
		\Huge{\textcolor{white}{Thank you for your attention!}}
	\end{center}
\end{frame}

\end{document}
